---
title: "Penguins"
author: "Yuxue Zhu"
date: 2026-09-24
---

# Introduction

In this post, I explore the `palmerpenguins` dataset using R. I focus on penguin species, body mass, and flipper length.

**Data source:** [palmerpenguins](https://allisonhorst.github.io/palmerpenguins/)

# Setup

Load the packages needed for the analysis. I suppress messages and warnings so that the rendered page focuses on the analysis.

```{r}
#| message: false
#| warning: false

library(palmerpenguins)
library(dplyr)
library(ggplot2)
```

# Exploring the data

First, check the structure of dataset.

```{r}
head(penguins)
```

The dataset contains 344 observations and 8 variables.

Next, calculate the number of penguins and average body mass for each species.

```{r}
species_summary <- penguins |>
  group_by(species) |>
  summarise(
    n = n(),
    mean_body_mass_g = mean(body_mass_g, na.rm = TRUE),
    sd_body_mass_g = sd(body_mass_g, na.rm = TRUE)
  )

species_summary
```

The summary shows differences in body mass among the three species. Gentoo penguins have the highest average body mass, while Adelie penguins have the lowest.

# Visualizing body mass

Create a boxplot to compare body mass across species.

```{r}
#| label: fig-penguin-mass
#| fig-cap: "Body mass of penguins by species."

ggplot(penguins, aes(x = species, y = body_mass_g)) +
  geom_boxplot() +
  labs(
    x = "Species",
    y = "Body mass (g)",
    title = "Penguin Body Mass by Species"
  ) +
  theme_minimal()
```

The figure shows that Gentoo penguins generally have greater body mass than Adelie and Chinstrap penguins.

# Flipper length and body mass

Calculate the correlation between flipper length and body mass.

```{r}
cor(
  penguins$flipper_length_mm,
  penguins$body_mass_g,
  use = "complete.obs"
)
```

The positive correlation indicates that penguins with longer flippers tend to have greater body mass.

# Conclusion

The analysis shows differences in body mass among penguin species. Gentoo penguins generally have the greatest body mass, and penguins with longer flippers tend to be heavier.
